---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bowlingpin

<!-- badges: start -->
<!-- badges: end -->

The "bowlingpin" package provides functions to calculate and display bowling scores for players based on their throws. It includes a function to calculate scores and another to format the results into a custom vector format. Additionally, the package ensures validation of input data and offers clear documentation with usage examples. 
The "max_gutters" function of bowlingpin package compares the number of gutters between players rolls and determines which player had the most, providing a message with the player's identifier and the count of gutters. 
The "max_strikes" function compares the number of strikes between two players rolls and identifies the player with the highest count, providing a message indicating the player and the number of strikes they achieved. 
The "bowling_winner" function determines the winner of a bowling game between players based on their scores, showcasing the victorious player's identity. 
The "player_throws" function manages player throws in a ten-pin bowling game, ensuring compliance with game rules by accepting player numbers, throws (as a list), and optionally, scores. Thorough validation checks are performed to ensure the integrity of input data. Additionally, "format.throws" facilitates the presentation of bowling scorecards, organizing player throws and scores into a structured and visually comprehensible format. 


## Installation

You can install the development version of bowlingpin from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Advanced-R-Programming/assignment-3-package-completion-Disharathod13")
```

## Example

This is a basic example which shows you how to use the bowlingpin function.
```{r example1}
library(bowlingpin)
player_rolls <- player_throws(player_no = c(1, 2, 3),
 throws = list(
 c(2, 3, 4, 5, 6, 4, 8, 1, 1, 2, 3, 4, 5, 5, 7, 2, 9, 1, 4, 6, 10),
 c(2, 3, 4, 5, 6, 4, 8, 1, 1, 2, 3, 4, 5, 5, 7, 2, 9, 1, 4, 3),
 c(1, 2, 3, 4, 5, 3, 1, 8, 9, 1, 2, 3, 4, 5, 2, 7, 8, 1, 10, 0, 10)
  ))
bowlingpin(player_rolls)
```


This is a basic example which shows you how to use the max_gutters function.
```{r example2}
 library(bowlingpin)
 player1_rolls <- c(0, 0, 3, 0, 0, 0, 7, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
 player2_rolls <- c(0, 0, 0, 0, 0, 0, 0, 0, 6, 0, 0, 0, 0, 0, 0, 4, 0, 0, 0, 0)
max_gutters(player1_rolls, player2_rolls)
bowlingpin(player_rolls)
```

This is a basic example which shows you how to use the max_strikes function.
```{r example3}
library(bowlingpin)
 player1_rolls <- c(10, 3, 4, 10, 5, 10, 7, 2, 3, 4, 10, 10, 10, 6, 7, 8, 9, 1, 2, 3)
 player2_rolls <- c(10, 10, 4, 3, 5, 10, 10, 2, 3, 4, 10, 10, 10, 6, 7, 8, 9, 1, 2, 3)
max_strikes(player1_rolls, player2_rolls)
```


This is a basic example which shows you how to use the bowling_winner function.
```{r example4}
library(bowlingpin)
  player_rolls <- player_throws(player_no = c(1, 2, 3),
 throws = list(
 c(2, 3, 4, 5, 6, 4, 8, 1, 1, 2, 3, 4, 5, 5, 7, 2, 9, 1, 4, 6, 10),
 c(2, 3, 4, 5, 6, 4, 8, 1, 1, 2, 3, 4, 5, 5, 7, 2, 9, 1, 4, 3),
 c(1, 2, 3, 4, 5, 3, 1, 8, 9, 1, 2, 3, 4, 5, 2, 7, 8, 1, 10, 0, 10)
 ))
 bowling_winner(player_rolls)
```


This is a basic example which shows you how to use the player_throws function.
```{r example5}
library(bowlingpin)
 player_rolls <- player_throws(player_no = c(1, 2, 3),
 throws = list(
 c(2, 3, 4, 5, 6, 4, 8, 1, 1, 2, 3, 4, 5, 5, 7, 2, 9, 1, 4, 6, 10),
 c(2, 3, 4, 5, 6, 4, 8, 1, 1, 2, 3, 4, 5, 5, 7, 2, 9, 1, 4, 3),
 c(1, 2, 3, 4, 5, 3, 1, 8, 9, 1, 2, 3, 4, 5, 2, 7, 8, 1, 10, 0, 10)
 ))
```


