---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bowlingpin

<!-- badges: start -->
[![R-CMD-check](https://github.com/numbats/assignment-1-package-creation-Disharathod13/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/numbats/assignment-1-package-creation-Disharathod13/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The "bowlingpin" package provides a function to simulate a ten-pin bowling game between two players, calculating their final scores based on their rolls. It accounts for strikes, spares, and open frames in each player's ten frames, returning their scores(Although, the scores for strikes and spares are not doubled as the exact real-game, but we will focus on that in the next update of this package). This package is a convenient tool for analyzing and comparing bowling performances between players in a simple and efficient manner.

## Installation

You can install the development version of bowlingpin from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("numbats/assignment-1-package-creation-Disharathod13")
```

## Example

This is a basic example which shows you how to calculate total scores of a ten pin bowling game for 2 players.

```{r example1}
library(bowlingpin)
player1_rolls <- c(2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)
player2_rolls <- c(2,2,2,2,8,2,6,2,2,2,2,2,5,2,2,2,4,2,2,3)
bowlingpin(player1_rolls,player2_rolls)
```

You can also use rollinput function to enter the scores for each throw in each frame for each player and use the output from that for calculating the final score.
